### 2013-10-11 Rcode/intro.rmd
modified default prior to uniform; changed name of sigmaavec to mixsd

Compare with mixfdr. Note that I tried to do small than 1000, but mixfdr returned
errors.
```{r}
ss = simdata(1000,800,0,2,1)

@@

mean((beta.ash$PosteriorMean-ss$beta)^2)

@@

Of course, if we do something where alternatives are not centered on 0 then
ash does worse!
```{r}
#This is the example from the mixfdr demo
z = c(rnorm(1000), rnorm(100,3,1))
 m = mixFdr(z, J = 3, noiseSD = 1)
 s = seq(-5,5,by=0.01)
 effCurve = effectSize(s,m)[,1]
 fdrCurve = fdrMixModel(s,m,abs(m$mu - m$mu[1])<=0.2) # this tells it which indices to consider null

@@

@@

Some advantages of the unimodal constraint:
-more statsitically efficient (if true); show with small sample sizes.
- less sensitive to number of components? Can allow number to tend to infinity?
- may be less sensitive to local optima?
- it allows us to easily just vary sigma on a grid, and fit pi, which
makes allowing different noise levels really easy!

@@

beta.ash=ash(ss$betahat,ss$betasd,auto=FALSE)
beta.ash.auto = ash(ss$betahat, ss$betasd,auto=TRUE)
#these to test the VB version 
beta.ash.vb.uniform = ash(ss$betahat, ss$betasd,auto=TRUE, VB=TRUE, prior="uniform")
beta.ash.vb.null = ash(ss$betahat, ss$betasd,auto=TRUE, VB=TRUE, prior=NULL)

@@

Now, we find the fitted values for $\pi$ are mostly near 0, or at 2 (the alternative value).
```{r}
summary(beta.ash)
summary(beta.ash.auto)
summary(beta.ash.vb.uniform)
summary(beta.ash.vb.null)
summary(beta.ash.pm)
```

@@

Let's try: 
```{r}
beta.ash.pm = ash(ss$betahat, ss$betasd, auto=TRUE, usePointMass=TRUE)
print(beta.ash.pm)
print(beta.ash.auto)
plot(beta.ash.auto$localfsr,beta.ash.pm$localfsr,main="comparison of ash localfsr, with and without point mass",xlab="no point mass", ylab="with point mass",xlim=c(0,1),ylim=c(0,1))
abline(a=0,b=1)
abline(a=0,b=2)
```

>>>>

Compare with mixfdr. Note that I tried to do smaller than 1000, but mixfdr returned
errors. (Maybe this example is not so useful for comparing fdrs (as opposed to shrinkage), since the methods tend to agree where the fdr is small, which is what matters?)
```{r}
ss = simdata(1000,500,0,2,1)

@@

mean((beta.ash$PosteriorMean-ss$beta)^2)
mean((beta.ash.u$PosteriorMean-ss$beta)^2)
mean((beta.ash.hu$PosteriorMean-ss$beta)^2)

@@

Of course, if we do something where alternatives are not centered on 0 then
ash does worse!
```{r}
#This is the example from the mixfdr help example
z = c(rnorm(1000), rnorm(100,3,1))
 m = mixFdr(z, J = 3, noiseSD = 1)
 s = seq(-5,5,by=0.01)
 effCurve = effectSize(s,m)[,1]
 fdrCurve = fdrMixModel(s,m,abs(m$mu - m$mu[1])<=0.2) # this tells it which indices to consider null

@@

Checking coverage
```{r}

@@

- unimodal distributions could be argued to be a primary motivation for shrinkage

- bayesian coverage intervals (attempt to) give much stronger guarantess than standard confidence intervals. Eg among the 0.95 intervals excluding 0,
less than 5% should actually be 0?

Some advantages of the unimodal constraint:
-more statsitically efficient (if true); show with small sample sizes.
- less sensitive to number of components? Can allow number to tend to infinity?
- may be less sensitive to local optima?
could demonstrate this by looking at convergence more carefully, and comparing
results with random starting points.

- it allows us to easily just vary sigma on a grid, and fit pi, which
makes allowing different noise levels really easy!

## The number of components is not critical

OR - this section could be more generally about selecting between
models (normal, uniforms etc) using log-likelihood.

Don't need to worry about overfitting - only need to worry
about whether model is "complex enough".

Because of the uni-modal constraint, the number of mixture components
is generally not critical, at least provided it is ``sufficiently large". 
Indeed, as the number of components tends to infinity, the likelihood
is bounded above, and the procedure will converge to a sensible limit.
The following example illustrates this.
We take 100 observations from 0.5N(-1,1)+0.5N(1,1)
and add N(0,1) noise.
```{r}
sampsize=500
beta = c(rnorm(sampsize,-1,1),rnorm(sampsize,1,1))
betahat = beta+rnorm(2*sampsize)

beta.ash = ash(betahat,1)
beta.ash.u=list()
for(i in 1:10){
  beta.ash.u[[i]] = ash(betahat,1,mixcompdist="uniform",prior="uniform",sigmaavec = seq(0.1,5,length=10*i))
}

plot(beta.ash,-4,4,col=2)
x=seq(-4,4,length=1000)
lines(x,0.5*dnorm(x,-1,1)+0.5*dnorm(x,1,1),col=1)
for(i in 1:4){
lines(x,density(beta.ash.u[[i]],x),col=2+i)
}

plot(unlist(lapply(beta.ash.u,ashr:::get_loglik)))

```{r}
sampsize=5000
beta = c(rnorm(sampsize,-1,1),rnorm(sampsize,1,1))
betahat = beta+rnorm(2*sampsize)

beta.ash = ash(betahat,1)
beta.ash.u=list()
for(i in 1:10){
  beta.ash.u[[i]] = ash(betahat,1,mixcompdist="uniform",prior="uniform",sigmaavec = seq(0.1,5,length=10*i))
}

plot(beta.ash,-4,4,col=2)
x=seq(-4,4,length=1000)
lines(x,0.5*dnorm(x,-1,1)+0.5*dnorm(x,1,1),col=1)
for(i in 1:4){
lines(x,density(beta.ash.u[[i]],x),col=2+i)
}

plot(unlist(lapply(beta.ash.u,ashr:::get_loglik)))

@@

beta.ash=ash(ss$betahat,ss$betasd,auto=FALSE)
beta.ash.auto = ash(ss$betahat, ss$betasd,auto=TRUE)
#these to test the VB version 
beta.ash.vb.uniform = ash(ss$betahat, ss$betasd,VB=TRUE, prior="uniform")
beta.ash.vb.null = ash(ss$betahat, ss$betasd,VB=TRUE, prior=NULL)

@@

@@

Let's try: 
```{r}
beta.ash.pm = ash(ss$betahat, ss$betasd, usePointMass=TRUE)
print(beta.ash.pm)
print(beta.ash.auto)
plot(beta.ash.auto$localfsr,beta.ash.pm$localfsr,main="comparison of ash localfsr, with and without point mass",xlab="no point mass", ylab="with point mass",xlim=c(0,1),ylim=c(0,1))
abline(a=0,b=1)
abline(a=0,b=2)
```
